Proposed Solution

### 2016-11-11 Ennan-Proposal/prelim.tex
stuff

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work on two configuration files given in 
Fig.~\ref{fig:twoFiles}. ConfigC first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these files we associated a list 
of templates. We then analyze {\emph {correct}} configuration files. When analyzing
a file, we first do type-checking, \ie we assign a type to every variable. 
We next instantiate each template with the typed variables and we save the learned set 
of rules. For instance, with integers we associate comparison templates, so after 
analyzing File$_1$, the set of learned rules will contain:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules is changing with every file that we analyze: contradicting 
files are removed and new rules are added. In practice, this process is done 
in parallel.

>>>>

From ConfigC we drew the main inspiration for this proposal. We now briefly
outline how does ConfigC work. It first automatically
analyzes a dataset of correct configuration files to derive
 rules for describing a specification. Before that process even starts,
we identified several basic types, 
such Boolean, Integer, File. With each of these files we associated a 
list of templates. We then analyze the given training data set of 
correct configuration files and derive rules describing variable 
relations. We demonstrate how it works on two fragments of configuration 
files given in Fig.~\ref{fig:twoFiles}.  When analyzing
a file, we first do type-checking, \ie we assign a type to every variable. After that we instantiate each template with the typed variables and we save the learned set 
of rules. For instance, with the integer type we only associated comparison templates ($X < Y, X = Y, \ldots$). After 
analyzing File\_1, the set of learned rules will contain the following rules:
\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
max_connections=300
mysql.max_persistent=200
max_connections > mysql.max_persistent
\end{lstlisting}
The set of learned rules is changing with every file that we analyze: contradicting 
files are removed and new rules are added. In practice, this process is done 
in parallel.
